%
% Daftar Pustaka 
% 

% 
% Tambahkan pustaka yang digunakan setelah perintah berikut. 
% 
\begin{thebibliography}{4}

\bibitem{drude}
{P. Drude. "Zur Elektronentheorie der Metalle."
\f{Ann. der Phys.} \bo{306 (3)}, 566 (1900)}

\bibitem{ashcroft-mermin}
{N. W. Ashcroft and N. D. Mermin. "Solid  State  Physics." Harcourt,Orlando (1976)}

\bibitem{kohn-sham}
{W. Kohn and L. J. Sham. "Self-Consistent Equations Including Exchange and Correlation Effects." \f{Phys. Rev.} \bo{A 140}, 1133 (1965)}

\bibitem{boer}
{J. H. de Boer and E. J. W. Verwey. "Semi-conductors with partially and with completely filled 3d-lattice bands." \f{Proc. Phys. Soc} \bo{49}, 59 (1937)}

\bibitem{mott}
{N. F. Mott and R. Peierls. "Discussion of the paper by de Boer and Verwey." \f{Proc. Phys. Soc} \bo{49}, 72 (1937)}

\bibitem{mott-hubbard}
{M. J. Rozenberg, G. Kotliar, and X. Y. Zhang. "Mott-Hubbard transition in infinitedimensions. II." \f{Phys. Rev. B} \bo{49}:10181–10193 (1994)}

\bibitem{antiferomagnetik1}
{J. E. Hirsch and S. Tang. "Antiferromagnetism in the Two-Dimensional Hubbard Model." \f{Phys. Rev. Lett} \bo{62}:591–594 (1989)}

\bibitem{d-wave}
{T. Yanagisawa. "Physics of the Hubbard model and high temperature supercon-ductivity." \f{JPCS} \bo{108}:012010 (2008)}

\bibitem{DMFT}
{A. Georges, G. Kotliar, W. Krauth, and M. J. Rozenberg. "Dynamical mean-fieldtheory of strongly correlated fermion systems and the limit of infinite dimensions." \f{Rev. Mod. Phys} \bo{68}:13–125 (1996)}

\bibitem{fetter}
{A.L. Fetter and J.D. Walecka. "Quantum Theory of Many-Particle Systems." \f{Dover Publications, Inc} (2003)}

\bibitem{spektral}
{C. Titchmarsh. “The theory of functions.” (1939)}

\bibitem{sokhotsi}
{Peter Henrici. "Applied and Computational Complex Analysis, vol. 3." \f{Willey, John $\&$ Sons, Inc.} (1986)}

\bibitem{ladder}
{R. Mattuck. "A guide to feynman diagram in the many-body problems." (1992)}

\bibitem{hubbard}
{J. Hubbard. “Electron correlations in narrow energy bands.” \f{Proceedingsof the Royal Society of London. Series A. Mathematical and Physical Sciences}, \bo{vol. 276}, no. 1365, pp. 238–257, (1963)}

\bibitem{mott-transition0}
{H. Strand. “Critical properties of the mott-hubbard metal-insulatortransition.” (2011)}

\bibitem{magnetic-excitation}
{M. Karski and G. U. C. Raas. “Single-particle dynamics in the vicin-ity of the mott-hubbard metal-to-insulator transition,” \bo{vol. 77}, no.7,p. 075116, (2008)}

\bibitem{mott-transition1}
{ J. Joo and V. Oudovenko. "Quantum Monte Carlo calculation of the finite tem-perature Mott-Hubbard transition." \f{Phys. Rev. B},  \bo{64}:193102,(2001) }

\bibitem{mott-transition2}
{R. Bulla, T. A. Costi, and D. Vollhardt. "Finite-temperature numerical renormal-ization group study of the Mott transition." \f{Phys. Rev. B}, \bo{64}:045103, (2001)}

\bibitem{mott-transition3}
{M. Capone, L. de’ Medici, and A. Georges.  "Solving the dynamical mean-fieldtheory at very low temperatures using the Lanczos exact diagonalization." \f{Phys.Rev. B}, \bo{76}:245116, (2007)}

\bibitem{mott-transition4}
{H. Strand, A. Sabashvili, M. Granath, B. Hellsing, and S. Östlund.  "Dynamical mean field theory phase-space extension and critical properties of the finitetemperature Mott transition." \f{Phys. Rev. B}, \bo{83}:205136, (2011)}

\bibitem{staudt}
{ R. Staudt, M. Dzierzawa, and A. Muramatsu. "Phase diagram of the three-dimensional Hubbard model at half-filling." \f{Eur. Phys.J.} \bi{B17}, 411 (2000) }

\bibitem{qmc_tn}
{ J. E. Hirsch. "Simulations of the three-dimensional Hubbard model: Half-filled band sector" \f{Phys. Rev.} \bo{B35} (1851) }

\bibitem{dmft_tn}
{ M. Jarrell. "Hubbard model in infinite dimensions: A quantum Monte Carlo study" \f{Phys. Rev. Lett} \bo{69}, 168 (1992). }

\bibitem{hartree_tn}
{ P. G. J. van Dongen. \f{Phys.Rev}. "Extended Hubbard model at weak coupling" \bo{B50}, 14016 (1994) }

\bibitem{heisenberg_tn}
{ G. S. Rushbrooke, G. A. Baker, and P. J. Wood. "in Phase Transitions and Critical Phenomena." edited by C. Domb and M. S. Green. \f{Academic Press, New York.} Vol. 3 (1974) }

\bibitem{qmc_tn2}
{ R. T. Scalettar, D. J. Scalapino, R. L. Sugar, and D. Tous-saint. "Phase diagram of the half-filled 3D Hubbard model." \f{Phys. Rev}. \bo{B39}, 4711 (1989) }

\bibitem{dmft_tn2}
{ M. Ulmke, V. Janis, and D. Vollhardt. "Anderson-Hubbard model in infinite dimensions" \f{Phys. Rev}. \bo{B51} 10411 (1995) }

\bibitem{metzner}
{ W. Metzner and D. Vollhardt. "Correlated Lattice Fermions in $d = \infty$ Dimensions." \f{Phys. Rev. Lett.}, \bo{62}:324–327, (1989) }

\bibitem{george}
{ A. Georges and G. Kotliar. "Hubbard model in infinite dimensions." \f{Phys. Rev. B}, \bo{45}:6479–6483, (1992) }

\bibitem{hfqmc}
{ J. E. Hirsch and R. M. Fye.  "Monte Carlo Method for Magnetic Impurities in Metals." \f{Phys. Rev. Lett.}, \bo{56}:2521–2524, (1986) }

\bibitem{ctqmc}
{ P. Werner, A. Comanac, L. de’ Medici, M. Troyer, and A. J. Millis. "Continuous-Time Solver for Quantum Impurity Models." \f{Phys. Rev. Lett.}, \bo{97}:076405, {2006} }

\bibitem{nrg}
{ K. G. Wilson. "The renormalization group: Critical phenomena and the Kondo problem." \f{Rev. Mod. Phys.}, \bo{47}:773–840, (1975) }

\bibitem{dmrg}
{  Steven R. White. "Density matrix formulation for quantum renormalization groups." \f{Phys. Rev. Lett.}, \bo{69}:2863–2866, (1992) }

\bibitem{ipt}
{ H. Kajueter and G. Kotliar. "New Iterative Perturbation Scheme for Lattice Modelswith Arbitrary Filling." \f{Phys. Rev. Lett.}, \bo{77}:131–134, (1996) }

\bibitem{nca}
{ H. Keiter and J. C. Kimball. "Perturbation Technique for the Anderson Hamilto-nian." \f{Phys. Rev. Lett.}, \bo{25}:672–675, (1970) }

\bibitem{sublattice}
{ R. Chitra and G. Kotliar. "Dynamical Mean Field Theory of the Antiferromagnetic Metalto Antiferromagnetic Insulator Transition." \f{Phys. Rev. Lett.} \bo{83}, 2386, (1999) }

\bibitem{kent}
{ P. R. C. Kent, M. Jarrell, T. A. Maier, and Th. Pruschke. "Efficient calculation of the antiferromagnetic phase diagram of the 3D Hubbard model" \f{arXiv:}\bo{cond-mat}/0506337, (2005) }

\bibitem{rohringer}
{G. Rohringer, A. Toschi, A. Katanin, and K. Held. "Critical properties of the half-filled Hubbard model in three dimensions" \f{Phys.Rev.Lett.} \bo{107}, 256402 (2011) }

\bibitem{daniel}
{ Daniel Hirschmeier, Hartmut Hafermann, Emanuel Gull, Alexander I. Lichtenstein, and Andrey E. Antipov. "Mechanisms of finite-temperature magnetism in the three-dimensional Hubbard model" \f{Phys. Rev. B}, \bo{92}, 144409 (2015)s }

\bibitem{dca}
{M.H. Hettler, M. Mukherjee, M. Jarrell, H.R.Krishnamurthy. "Dynamical cluster approximation: Nonlocal dynamics of correlated electron systems" \f{Phys. Rev. B} \bo{61}, 19,(2000)}

\bibitem{anna}
{Anna Golubeva, Andrii Sotnikov, and Walter Hofstetter. "Effects of anisotropy in simple lattice geometries on many-body properties of ultracold fermions in optical lattices" \f{Phys. Rev. A}, \bo{92}, 043623 (2015)} 

\bibitem{mf}
{ Yann Claveau, Brice Arnaud, and Sergio Di Matteo. "Mean-field solution of the Hubbard model: the magnetic phase diagram" \f{ 	arXiv:}\bo{1403}.2259, (2014) }

\bibitem{el-ph}
{ J. Millis, Boris I. Shraiman and R. Muelle. "Dynamic Jahn-Teller effect and colossal magnetoresistance in La$_{1-x}$Sr$_x$MnO$_3$." \f{Phys. Rev. Lett}. \bo{77} 1, (1996) }

\bibitem{hund}
{N. Furukawa. "Thermodynamics of Double Exchange." \f{J.Phys.Soc.Japan} \bo{63} 3214, (1994)}

\end{thebibliography}

